\chapter{Conclusion}
The main goal set out by the team from the beginning was to create a unique platform for students in the Galway area to both advertise and search for accommodation. Concluding the project, as a team we can say the goal has been achieved in the form of a web-application exclusively for students local to Galway. 

\paragraph{}
\textbf{UniLodge} is intended to fill the market gap that was identified during the research phase. The finding showed there was no service for students to exclusively interact and advertise accommodate services. As a team we hope that by developing this service we can help bridge the gap between the two parties that previously had no access to a platform of this nature.

\section{Key Insights \& Learning Outcomes}
Along the way, a wide range of learning outcomes and insights were gained, with most of them encountered indirectly and unexpectedly. This section will highlight and discuss the key insights acquired by the team.

\begin{description}
  \item[$\bullet$] \textit{\textbf{The Importance of Testing}}.
  
  \paragraph{}
  \textbf{T}he team knew testing was an important part of building a robust system, however had to learn the hard way how vital it was in ensuring unexpected blockers and outcomes didn't outright halt and disrupt development.
  
  \paragraph{}
  In future, more time and resources will undoubtedly be dedicated towards testing, the team saw first hand the missed investment and the associated result of not incrementally testing. \newpage
  
  \item[$\bullet$] \textit{\textbf{Working with Diverse Technologies}}.
  
  \paragraph{}
  \textbf{W}hile Angular, Flask, Python and MongoDB aren't exactly uncommon names to see in development stacks, working with specifically those names was found to be a rocky experience during the initial development phase. As it turned out, there wasn't a whole lot of content to be found integrating those three technologies.
  
  \paragraph{}
  To get a handle on how to assemble the stack meant reading through base level documentation to try and figure out where and how everything would fit together. Unfortunately, there was no cookie cutter method to get everything set up unlike there would be when working with a traditional MEAN stack. 
  
  \paragraph{}
  However the importance of effective research and documentation analysis was picked up, allowing the inclusion and wiring together of other components (\textit{albeit unintentional and unexpected}) and different methods of integrating them.

  \item[$\bullet$] \textit{\textbf{The Effect of Communication during Development}}.
  
  \paragraph{}
  \textbf{U}nfortunately, internal communication issues did cause disruption during the project cycle. This would ultimately lead to loose ends, unfulfilled commitments and ambiguity surrounding major elements of the project. As a result, the scope of the project had to frequently be readjusted and redefined, leading to constant backlogs and ultimately features that wouldn't see implementation before the deadline. 
  
  \paragraph{}
  Even though it may seem obvious from an outside view that effective communication is essential within a project, experiencing and having to adapt to it first-hand really did highlight its importance within an effective team. 
  
  \item[$\bullet$] \textit{\textbf{Consultation with End Users}}.
  
  \paragraph{}
  \textbf{T}he team were very fortunate to have access to a wide range of potential end users during development. While the initial base-vision for the overall system was defined at an early stage, constant input from fellow students helped shape the vision into something tailored and specialized towards a specific target audience.
\end{description}

\paragraph{}
The highlighted conclusive insights consist of a handful of outcomes that the team consider to be some of the more valuable takeaways from the project. As a team, our goal for the future is to take the highlighted outcomes as well as those passively attained and apply them to any future tasks.

\section{Future Development}
While the project objectives and goals were met, there is undoubtedly still room for growth. This section will outline some key areas that will definitely see future development, the features will consist of components that couldn't be implemented due to time constraints or features that the team feel would be practical additions.

\subsection{Browsing Features}
A list of search enhancing features were recommended by others and considered by the team during development, a brief description of each of these features to be developed in the future will be described here.

\subsubsection{GPS Functionality}
A potential inclusion the team felt excited about was an interactive map that would enable the user to search for nearby listings based on their location, or even compare the distance between the listing and their educational institute.

\subsubsection{More Listing Depth}
Currently the information available on individual listings is limited. In future iterations more specific content would ideally be included, like how long the location is available for or closest educational institute for example.

\subsubsection{More Browse Functionality}
When browsing for listings currently, two parameters may be used for searching, price and location. In future, including parameters that allow to sort by date posted, poster and potentially rating would be ideal.

\subsection{User Features}
Features that would enhance the overall experience of the user are considered to be some of the more important potential inclusions for future development, some of the more important features will be described below.

\subsubsection{Profile Customization}
More details about the user would give more depth to the overall application. Inclusions like positive or negative reputation, previous postings or page views would enhance the overall user experience and by extension the overall service.

\subsubsection{Follow Feature}
The ability to 'follow' other users and be notified of relevant actions taken by that user was a feature that was heavily considered at early stages. Following discussions with other students, the overwhelming majority of those consulted concluded that other features like browsing or commenting were far more important and should take precedence.

\subsubsection{Private Messaging}
While users can communicate through comments and organize between themselves their conditions or follow up with more detailed conversation through a phone call or text message, an ideal scenario would allow both parties to discretely message each other when discussing more sensitive topics.

\subsection{Miscellaneous Features}

\subsubsection{Mobile Friendly}

\subsubsection{}

\section{Final Thoughts}